Free surface computations in mantle convection models

### 2015-10-05 free-surface-paper.tex
Add AMR figure to manuscript

>>>>

We also investigate the advantages of combining adaptive mesh refinement with free surface computations.
\citet{crameri2012comparison} performed a community benchmark of a setup for which there is no analytic
solution. In this benchmark, a buoyant blob rises beneath a viscous lid with a free surface, deflecting the
boundary upwards (for the full setup, see \citet{crameri2012comparison}). 
Figure~\ref{fig:amr} shows the convergence of the maximum topography at 3 Myr to its value in a high resolution simulation.
Figure~\ref{fig:amr}a shows the convergence with uniform refinement, and~\ref{fig:amr}b shows the convergence
with adaptive mesh refinement. Both have essentially the same behavior, but the adaptive case requires 
fewer degrees of freedom by a factor of approximately an order of magnitude. More complex models will have
more detail and so we may be less able to aggressively coarsen them, but we still expect that adaptive mesh refinement 
will result in significant computational savings.

\begin{figure*}
\includegraphics[width=0.9\textwidth]{figures/amr.pdf}
\caption{Convergence with resolution for the \citet{crameri2012comparison} Case 2 benchmark, for both uniform (a) and adaptive (b) mesh refinement. The minimum cell size h is normalized by the model depth, and the timestep $\Delta t$ is 500 yr. We compare the maximum topography at 3 Myr with its value at high resolution ($\sim$398 m). The points are labeled with the approximate number of degrees of freedom (DoFs) for that simulation. Both cases converge similarly, but the adaptive mesh refinement simulations require significantly smaller system sizes.}
\label{fig:amr}
\end{figure*}
